\section{A math professor is interested in the relationship between students’ performance on the
    first midterm in his class and their performance on the second midterm in his class. He
    gathers the midterm 1 and midterm 2 data for his $n = 112$ students (this data is called
    “Midterm1” and “Midterm2” respectively in the “Bonus Assignment Data” R file). Note that
    the scores for both midterm 1 and midterm 2 are out of $100$ points.}
    \begin{multicols}{2}
        \subsection{Creat a scatterplot of the data. Describe the general relationship (trend) 
            of the midterm 1 and midterm 2 scores.}
            %See figure \ref{fig:1a} on page \pageref{fig:1a}.
            \begin{center}  
                \input{r/tikzDevice/1a.tex}
            \end{center}

        \subsection{What is the correlation between midterm 1 grades and midterm 2 grades? Interpret
            this correlation.}
            $r \approx 0.5048535$

        \subsection{State the least-squares estimate of the model predicting midterm 2 scores from
            midterm 1 scores.}
            $m_2 \approx 0.6619698m_1 + 26.0843211$

        \subsection{Interpret the slope of this regression equation in the context of the data.}
            For every 1 point increase on a student's score on midterm 1, 
            there will be a 0.6620 point increase on the student's score on midterm 2.

        \subsection{Predict the midterm 2 score of a student who scored 60 on midterm 1.}
            $m_2 \approx 0.6619698m_1 + 26.0843211$\\
            $= 0.6619698(60) + 26.0843211 \approx 65.80$

        \subsection{Predict the midterm 2 score of a student who scored 92 on midterm 1.}
            $m_2 \approx 0.6619698m_1 + 26.0843211$\\
            $= 0.6619698(92) + 26.0843211 \approx 86.99$

        \subsection{Suppose a student scored a 80 on\\
            midterm 1. Calculate the residual for this student if
            they also scored an 80 on midterm 2.}
            $\epsilon = m_2 - \hat m_2 \approx 80 - (0.6619698m_1 + 26.0843211)$\\
            $= 80 - (0.6619698(80) + 26.0843211) \approx 0.9581$

        \subsection{Assuming the normality condition is met, what would you expect the normal
            probability plot of the residuals to look like? Describe it in words or draw a picture.}
            See figure \ref{fig:1h} on page \pageref{fig:1h}.\\
            The historgram is close to normal. 
            On the normal probabily plot, the dots are close to the lines.

        \subsection{Conduct a hypothesis test to determine if midterm 2 scores can be expressed as a linear
            function of midterm 1 scores. Please state all steps of the hypothesis testing process
            (hypotheses, test statistic, p-value, conclusion). Use $\alpha = 0.05$.}
            $H_0: \beta_1 = 0, H_a: \beta_1 \neq 0$\\
            $t = \frac{\beta_1 - \beta_{1_0}}{SE_{\beta_1}} 
            \approx \frac{0.662 - 0}{0.107917} \approx 6.134$\\
            $\pv = 2 * (1 - pt(t, 110)) \approx 1.377 * 10^{-8} < 0.05 = \alpha$\\
            Therefore there is a linear dependency of the score on midterm 1
            on midterm 2.

        \subsection{Construct a $95\%$ confidence interval for the slope. Does this confidence interval suggest
            that the slope is significantly different from zero?}
            Confidence interval: (0.4481033, 0.8758362). \\
            Yes, it does not contain 0.
    \end{multicols}