\section{R has a built-in dataset called {\color{red} trees} that contains observations for 
    $n = 31$ black cherry
    trees. The first column, “Girth,” contains the girth of the trees (in inches); the second
    column, “Height,” contains the height of the trees (in feet); the third column, “Volume,”
    contains the volume of timber (in cubic feet).}
    \begin{multicols}{2}
        \subsection{State the least-squares estimate of the model predicting diameter from height.}
            (Note: Diameter is mislabeled as girth in the dataset.)\\
            $d$ and $h$ are in inches: $d \approx 0.02131h-6.188$

        \subsection{Predict the diameters of trees of the following heights: 
            $60$ feet, $73$ feet, and $85$ feet.}
            In inches.\\
            Height of 60 feet: \\
            $d \approx 0.02131226 (60 * 12)-6.18839451$
            $\approx 9.156$\\
            Height of 73 feet: \\
            $d \approx 0.02131226 (73 * 12)-6.18839451$
            $\approx 12.48$\\
            Height of 85 feet: \\
            $d \approx 0.02131226 (85 * 12)-6.18839451$
            $\approx 15.55$

        \subsection{Interpret the meaning of the slope in the context of the data.}
            For every 1 inch increase the height, 
            there will be a 0.02131 inch increase in diameter.

        \subsection{Suppose you wanted to conduct a hypothesis test for a positive linear relationship
            between height and diameter. State the appropriate hypotheses and test statistic.}
            $H_0: \beta_1 \leq 0, H_a: \beta_1 > 0$\\
            $t = \frac{\beta_1 - \beta_{1_0}}{SE_{\beta_1}}
            \approx \frac{0.02131226 - 0}{ 0.006513191} \approx 3.272$

        \subsection{State the probability expression of the p-value as well as the p-value itself. What
            conclusion would we reach with respect to our hypotheses in part d. using $\alpha = 0.05$?}
            $\pv = P(T_{df} > 3.272\hdots) = 1 - pt(t, df) 
            \approx 0.1379\% < 5\% = \alpha$\\
            Therefore there is a linear dependency of height on diameter.

        \subsection{If you wanted to report a $95\%$ interval for the diameter of a single tree that was $80$
            feet tall, would you report a confidence interval or prediction interval? Why?}
            Prediction interval, as it predicts the dependent variable 
            from a given independent variable\\
            Prediction interval: (13.08276, 15.45999 ) in inches.

        \subsection{What proportion of $\sigma^2$ in diameter is explained by its linear relationship with
            height?}
            $r^2 \approx 0.2697$

        \subsection{Examine the residual plot. What condition/assumption does the residual plot check for?
            Does it appear to be met in this case?}
            %See figure \ref{fig:3h} on page \pageref{fig:3h}.
            It checks for consistancy in variance. 
            In this case, yes, the points are in a random pattern.
            \begin{center}
                \input{r/tikzDevice/3h.tex}
            \end{center}
    \end{multicols}